Analysis for Biracial Grade Retention Project

### 2022-09-02 analysis/analysis.Rmd
Refactor calculate_marg_means into a separate subfuncion of create_coef_table
This will allow me to use all of that code even when I have a different method for getting the marginal means as for the counterfactual case

```{r create-cf-marg}
coefs <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows() %>%
  mutate(multiracial=str_detect(term, "/"))

coef_table <- map(as.list(str_subset(coefs$term, "/")), function(x) {
    coefs %>%
      filter(term %in% c(x, str_split(x, "/")[[1]])) %>%
      mutate(mrace=factor(x,
                          levels=c("Black/White",
                                   "White/Indigenous",
                                   "Latino/Asian",
                                   "Black/Latino",
                                   "White/Latino",
                                   "Indigenous/Latino",
                                   "Black/Asian",
                                   "White/Asian",
                                   "Indigenous/Asian",
                                   "Black/Indigenous")),
             estimate_mid=ifelse(multiracial, 
                                 mean(estimate[!multiracial]),
                                 estimate),
             se_mid=ifelse(multiracial, 
                                  sqrt(sum(se[!multiracial]^2)/4),
                                  se))
  }) %>%
    bind_rows()

  #get terms ordered
  race_names <- levels(reorder(factor(coef_table$term), coef_table$estimate))
  #pull out single race and multiple race as separate vectors
  race_single <- str_subset(race_names, "/", negate=TRUE)
  race_multi <- str_subset(race_names, "/", negate=FALSE)
  #start with single races
  race_full <- race_single
  #now loop through multiple race names and append based on the higher group
  for(race in race_multi) {
    temp <- str_split(race, "/")[[1]]
    idx <- max(which(race_full==temp[1]), which(race_full==temp[2]))
    race_full <- append(race_full, race, idx-1)
  }

  #now use this as the levels of term as a factor
  coef_table <- coef_table %>%
    mutate(term=factor(term, levels=race_full))
```

```{r counterfactual-ses, warning=FALSE, fig.cap="Counterfactual probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups if the only differences between groups were resources (household income, parental education, home ownership, parent and child foreign-born status, parent and child English proficiency, and whether parents are married). 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level."}
  ggplot(coef_table, aes(x=term, y=estimate, color=multiracial,
                         ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
    geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                  ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
              color=NA, alpha=0.2)+
    geom_linerange(data=subset(coef_table, multiracial))+
    geom_point()+
    coord_flip()+
    facet_wrap(~mrace, scales="free_y")+
    theme_bw()+
    theme(legend.position = "none", panel.grid = element_blank())+
    scale_color_manual(values=c("grey40","red"))+
    scale_fill_manual(values=c("grey40","red"))+
    scale_linetype_manual(values=c(3,1))+
    scale_y_continuous(labels = scales::percent)+
    labs(x=NULL,
         y="average adjusted predicted probability of being behind expected grade")

>>>>

```{r create-cf-marg}
coefs <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

coef_table_cf <- create_coef_table(coefs)
```

```{r counterfactual-ses, warning=FALSE, fig.cap="Counterfactual probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups if the only differences between groups were resources (household income, parental education, home ownership, parent and child foreign-born status, parent and child English proficiency, and whether parents are married). 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level."}
  ggplot(coef_table_cf, aes(x=term, y=estimate, color=multiracial,
                         ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
    geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                  ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
              color=NA, alpha=0.2)+
    geom_linerange(data=subset(coef_table_cf, multiracial))+
    geom_point()+
    coord_flip()+
    facet_wrap(~mrace, scales="free_y")+
    theme_bw()+
    theme(legend.position = "none", panel.grid = element_blank())+
    scale_color_manual(values=c("grey40","red"))+
    scale_fill_manual(values=c("grey40","red"))+
    scale_linetype_manual(values=c(3,1))+
    scale_y_continuous(labels = scales::percent)+
    labs(x=NULL,
         y="average adjusted predicted probability of being behind expected grade")
